Supplementary Information

### 2021-03-02 doc/manuscript/ForestGEO_treerings.Rmd
misc
Update ForestGEO_treerings.Rmd

[Kristina J. Anderson-Teixeira](0000-0001-8461-9713)^1,2^*,
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Ross Alexander^5^,
Craig D. Allen^6^,
Raquel Alfaro-Sánchez^7^,
Tala Awada^8^,
Jennifer L. Baltzer^7^,
Patrick J. Baker^9^,
[Joseph D. Birch](0000-0001-8644-7345)^10^,
Sarayudh Bunyavejchewin^11^,
Paolo Cherubini^12^,
Stuart J. Davies^2^,
Cameron Dow^1,13^,
Ryan Helcoski^1^,
[Jakub Kašpar](0000-0003-1780-6310)^14^,
[James Lutz]( 0000-0002-2560-0710)^15^,
Ellis Q. Margolis^16^,
Justin Maxwell^17^,
Sean McMahon^2,18^,
Camille Piponiot^1,2,19^,
Sabrina Russo^8^,
[Pavel Šamonil](0000-0002-7722-8797)^14^,
Anastasia Sniderhan^7^,
Alan J. Tepley^1,20^,
[Ivana Vašíčková](0000-0002-6070-5956)^14^, 
Mart Vlam^21^,
Peter Zuidema^21^

@@

2. Center for Tropical Forest Science-Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama

>>>>

[Kristina J. Anderson-Teixeira](0000-0001-8461-9713)^1,2^*,
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Ross Alexander^5^,
Craig D. Allen^6^,
Raquel Alfaro-Sánchez^7^,
Tala Awada^8^,
Jennifer L. Baltzer^7^,
Patrick J. Baker^9^,
[Joseph D. Birch](0000-0001-8644-7345)^10^,
Sarayudh Bunyavejchewin^11^,
Paolo Cherubini^12^,
Stuart J. Davies^2^,
Cameron Dow^1,13^,
Ryan Helcoski^1^,
[Jakub Kašpar](0000-0003-1780-6310)^14^,
[James Lutz]( 0000-0002-2560-0710)^15^,
Ellis Q. Margolis^16^,
Justin Maxwell^17^,
Sean McMahon^2,18^,
Camille Piponiot^1,2,19^,
Sabrina Russo^8^,
[Pavel Šamonil](0000-0002-7722-8797)^14^,
Anastasia Sniderhan^7^,
Alan J. Tepley^1,20^,
[Ivana Vašíčková](0000-0002-6070-5956)^14^, 
Mart Vlam^21^,
Pieter Zuidema^21^

@@

2. Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama
